---
title: "Built a logistic regression model to predict customer churn in the Telecom industry"
author: "Swarup"
date: "13/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

####The primary objective was to investigate the parameters contributing for customer churn (attrition) in the Telecom Industry. A Logistic Regression Model was developed and validated with test data to predict customer churn.

#Loading the DataSet
```{r}
library(readxl)
mydata=read_xlsx(file.choose(),sheet = 2)
```
#Exploratory Data Analysis
```{r}
library(GGally)
library(dplyr)
glimpse(mydata)
```
#Structure of the Data Set
```{r}
str(mydata)
library(psych)
describe(mydata)
```
#Check NA values
```{r}
nacount=sapply(mydata,function(y)sum(is.na(y)))
nacount
#Change Churn,ContractRenewal,DataPlan to factor variables
attach(mydata)
mydata$Churn=as.factor(mydata$Churn)
mydata$ContractRenewal=as.factor(mydata$ContractRenewal)
mydata$DataPlan=as.factor(mydata$DataPlan)
```
##Observation
*No NA values found*
*Churn,ContractRenewal,DataPlan are converted to factor variables*

#Univariate Analysis

```{r}
#ggp=ggpairs(mydata[-c(1,3,4)], aes(color = mydata$Churn))+ theme_bw()
#print(ggp,progress=FALSE)
boxplot(mydata[-c(1,3,4)])
```
##Observation

*Outlier values found for all variables*

```{r}
#rosnerTest--Outlier Detection
```
#Bivariate Analysis
```{r}
ggp=ggpairs(mydata[-c(1,3,4)], aes(color = mydata$Churn))+ theme_bw()
print(ggp,progress=FALSE)
ggplot(mydata,aes(x=mydata$AccountWeeks,fill=Churn))+geom_histogram(binwidth = 50)
```

